---
title: "uniqueness of models use predicion variance column importance"
---
need to compare against best model to get competeing interesting ones
then separate using PCA? let allmodel decide if there is anything
!mincomb has been added
```{r}
  require(readr)
require(netCoin)
require(data.table)
require(naniar) 
require(VIM)
require(ggplot2)
```

first lets get the perfect goals and clean that set 
```{r}
 load(file="routPerfects.RData")
dim(Perf)
Perf<-unique(Perf,by=c("pq9TargRank","RMSEutrans","MAEutrans","transTarg","RMSEmean","RMSEmeantrain","seedit","transform","fold","task"))
dim(Perf)
Perf[(is.na(gainin30))]
Perf[(spearman2!=1)]
Perf<-Perf[(spearman2==1)]

#Does perfect greement between perfects matter? All 
#I need is perfect scores per item. the perfect scores seem the same but seed affects foldseed 222
Perf[,recifKey:=paste0(transTarg,task,transform,expirament,fold)]#seed seedit
Perf[,recifN:=.N,by=recifKey]
summary(Perf$recifN)
Perf[(recifN>1)][(order(recifKey))]

#assuming only one expirament task or else another outer loop will be needed
#also not really bothering with transformations bc work

prf<-data.table()
for(i in unique(Perf$task)){
  wrk<-Perf[(task==i)]
  wrk<-wrk[(transTarg==2)]
  #just because changes in code were made thispart shouldbeless necessarylater
  wkn<-wrk[(is.na(btp9))][,(44:163),with=F]
  wkf<-wrk[(!is.na(btp9))][,(41:160),with=F]
  wrk<-rbindlist(list(wkn,wkf),use.names =F)
  wrk<-unique(wrk)
  indx<-as.integer(unlist(wrk[,seq(by=2,from=1,to=dim(wrk)[2]),with=F]))
  val<-as.integer(unlist(wrk[,seq(by=2,from=2,to=dim(wrk)[2]),with=F]))
  unique(indx)
  unique(val)
  wrk<-data.table(indx,val)
  dim(wrk)
  wrk<-unique(wrk)
  if(dim(wrk)[1]!=length(unique(wrk$indx))) stop("more work, multiple valuse for same index")
  wrk<-wrk[(order(indx))]
  prf<-rbindlist(list(prf,wrk),use.names =T)
}
prf<-unique(prf)
  if(dim(prf)[1]!=length(unique(prf$indx))) stop("more work, multiple valuse for same index")
dim(prf)
```
load and fix uniq worthy tested models
```{r}
load(file="routuDFpessimistUnique.RData")
(bestest<-Unq[(1)])
nnd<-which(names(Unq)=="datePOSIX")
strt<-which(names(Unq)=="btp8")
Unqn<-Unq[(is.na(btp11))]
Unqf<-Unq[(!is.na(btp11))]
Unqf[,dum1:=0]
Unqf[,dum2:=0]
Unqf[,dum3:=0]
Unqn[,dum1:=0]
Unqn[,dum2:=0]
Unqn[,dum3:=0]
colord<-names(Unqf)
ol<-length(colord)
(colord<-c(colord[1:strt],colord[(ol-2):ol],colord[(strt+1):(nnd-4)],colord[(nnd):(ol-3)]))
setcolorder(Unqf,colord)

```


```{r}
  why<-rbindlist(list(Unqn,Unqf),use.names =F)
 why<-why[(transTarg==2)]
 strt<-which(names(Unq)=="X47")
nnd<-which(names(Unq)=="datePOSIX") -1
 why[,keyErrors:=paste0(keyMiss,algomodel)]

prd<-data.table(trg=prf$val)
i<-unique(why$keyErrors)[1]

for(i in unique(why$keyErrors)){
  wrk<-why[(keyErrors==i)][,(strt:nnd),with=F]
  wrk<-unique(wrk)
  indx<-as.integer(unlist(wrk[,seq(by=2,from=1,to=dim(wrk)[2]),with=F]))
  val<-as.integer(unlist(wrk[,seq(by=2,from=2,to=dim(wrk)[2]),with=F]))
  unique(indx)
  unique(val)
  wrk<-data.table(indx,val)
  wrk$val<-as.numeric(wrk$val)
  dim(wrk)
  wrk<-wrk[(order(indx))]
  wrk[,sdw:=sd(val),by=indx]
  wrk[,Nw:=.N,by=indx]
  wrk[,val:=mean(val),by=indx]
  wrk<-unique(wrk)
  if(dim(wrk)[1]!=length(unique(wrk$indx))) stop("more work, multiple valuse for same index")
  prd[wrk$indx,paste0(i,"val"):=wrk$val]
  prd[wrk$indx,paste0(i,"sd"):=wrk$sdw]
}
prd
length(names(prd))#removed transformed target so not 601
names(prd)[c(1,2,3,6,7,8,15,16,17)]

require(stringr)
vals<-str_detect( names(prd), "val")
sds<-str_detect( names(prd), "sd")
```
like time series of each; red dot vs lots of other colors. orered by trg. must make mean?

```{r}
vals[1]<-F
prd[,medi:=0]
prd$medi<-apply(prd[,vals,with=F],1,median,na.rm=T)
prd[,men:=0]
prd$men<-apply(prd[,vals,with=F],1,mean,na.rm=T)
prd[,ninfi:=0]
prd$ninfi<-apply(prd[,vals,with=F],1,quantile,.95,na.rm=T)
prd[,ofif:=0]
prd$ofif<-apply(prd[,vals,with=F],1,quantile,.05,na.rm=T)
vals[1]<-T
ggplot(prd[(order(medi))][(order(trg))], aes(x=1:dim(prd)[1])) + geom_point(aes(y=medi),color="green") + geom_point(aes(y=trg),color="red") + 
geom_point(aes(y=ninfi),color="blue") +
geom_point(aes(y=ofif),color="blue") +
geom_point(aes(y=QSlinks115_60centernscale2QSlink3regr.randomForestval
,color="yellow"))
vals[1]<-F
ggplot(prd, aes(x=as.factor(trg))) +
geom_boxplot(aes(y=QSlinks115_60centernscale2QSlink3regr.randomForestval))
```
corrplot; intermodel correlations usualy bigger than target
```{r}
vals[1]<-T
require(corrplot)
M<-cor(prd[,vals,with=F],use="pairwise.complete.obs",method = "spea")
corrplot(M[1:20,1:20],tl.cex	=.45)
vals[1]<-F
```
some models are bad with exact valuse but their spearman and pearson are fantasic. maybe can draw spearman and pearson errors? basic normalization just does not do enough; because of skew, outliers? or just bas alaignment;
first check for NAs
```{r}

vals[1]<-T
prd[,vals,with=F][(dim(prd)[1])]
prd<-prd[(1:(dim(prd)[1]-1))]
prd[,vals,with=F][,2,with=F]
sum(is.na(prd[,vals,with=F]));dim(prd)[1] * dim(prd)[2] / 2
for(i in names(prd)){
  mpi<-mean(prd[,(i),with=F][[1]],na.rm = T)
  prd[(is.na(get(i))),c(i):=mpi]
  prd[(is.na(get(i))),c(i):=0]
  prd[,c(i):=round(get(i),digits = 3)]
  
}
sum(is.na(prd[,vals,with=F]));dim(prd)[1] * dim(prd)[2] / 2
prd
```

converting scores drectly to pearson cor and spearman cor errors
```{r}
vals[1]<-T
prd$trg<-as.numeric(prd$trg)
prdr<-prd[,vals,with=F]
prdn<-prd[,vals,with=F]
for(i in names(prdr)){ #i<-"QSlinks14_55all2QSlink3BstLmval"
  prdr[,c(i):=rank(get(i),na.last = "keep",ties.method = "average")]

  prdn[(!is.na(get(i))),c(i):=(get(i)-mean(get(i)))/sd(get(i))]  
  prdr[(!is.na(get(i))),c(i):=(get(i)-mean(get(i)))/sd(get(i))]
  prdn[(is.na(get(i))),c(i):=0]  
  prdr[(is.na(get(i))),c(i):=0]
  
  if(i!="trg"){
    prdn[,c(i):=(prdn$trg-get(i))^2]  
    prdr[,c(i):=(prdr$trg-get(i))^2]
  }
  prdn[,c(i):=round(get(i),digits = 3)]
  prdr[,c(i):=round(get(i),digits = 3)]
}
```
corrplot; intermodel correlations usualy bigger than target
```{r}

require(corrplot)
M<-cor(prdn,use="pairwise.complete.obs",method = "spea")
corrplot(M[1:20,1:20],tl.cex	=.45)
hist(as.vector(M))
M<-cor(prdr,use="pairwise.complete.obs",method = "spea")
corrplot(M[1:20,1:20],tl.cex	=.45)
hist(as.vector(M))
```
new datasets to MILL (does linear combo make anything?) #effectively stacking. though maybe I should have left that to tpt
```{r}

require(readr)
prdr$trg<-as.numeric(prd$trg)
prdn$trg<-as.numeric(prd$trg)
write_csv(prd[,1:190,with=F],path="routQSlinksStack.csv")
write_csv(prdr[,1:150,with=F],path="routQSlinksStackErrRankSqr.csv")
write_csv(prdn[,1:150,with=F],path="routQSlinksStackErrSqr.csv")
```

include min distance instead of l1 as a pessimism

then column importance in different notebook


does sd ever predict error?
if that colorfull graph is any indication then no
Else I should use ML for the 300x300 possible interactions

clustering & netgraph & PCA ICA 
first must check if this kind of stacking is ever useful by sending data to ml

??fix first and simple firts??