---
title: "Variable importance"
---
is the signal clean but containing rare usefullness or noisy and always present?

load all varimp files and check problems and remove some problems
```{r}
col_typed <- "cccddccccccddddddcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcdcd?????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????????"
#71 per row so 142+ more than 20?
#167
try({setwd(mainDir)})
mainDir<-getwd()
subDir<-"QSlinks_simple"
#dir.create(file.path(mainDir, subDir))
require(readr)
require(netCoin)
require(data.table)
require(naniar) 
require(VIM)
require(ggplot2)
require(stringr)

resultDir<-"ACEREBOUT"
#setwd(resultDir)
setwd(file.path(mainDir, resultDir))
QSlink3ACE <- read_csv("importanceQSlink3ACEREBOUTwindowsx64.csv",col_types = col_typed)
resetACE <- read_csv("test after which reset.csv")
names(resetACE)<-c("date","model","task","fold","cv","arch","arch2","pc")
#QSlinkImp3ACE <- read_csv("importanceQSlink3ACEREBOUTwindowsx64.csv",col_types = col_typed)
#summary(QSlink3ACE[,1:30])
 #spec(QSlink3ACE)
 prACE<-problems(QSlink3ACE)
 unique(prACE$actual)
 #prACE[!str_detect(prACE$actual,"columns"),]
 rowrem<-prACE[!str_detect(prACE$actual,"columns"),]$row
 QSlink3ACE<-QSlink3ACE[-rowrem,]
 setwd(file.path(mainDir))

 
 resultDir<-"HOPPER"
#setwd(resultDir)
setwd(file.path(mainDir, resultDir))
QSlink3HOP <- read_csv("importanceQSlink3HOPPERwindowsx64.csv",col_types = col_typed)
resetHOP <- read_csv("test after which reset.csv")
names(resetHOP)<-c("date","model","task","fold","cv","arch","arch2","pc")
#summary(QSlink3ACE[,1:30])
 #spec(QSlink3HOP)
 prHOP<-problems(QSlink3HOP)
 unique(prHOP$actual)
 #prHOP[!str_detect(prHOP$actual,"columns"),]
  rowrem<-prHOP[!str_detect(prHOP$actual,"columns"),]$row
 QSlink3HOP<-QSlink3HOP[-rowrem,]
 setwd(file.path(mainDir))
 #names(QSlink3HOP)
 
  resultDir<-"LAPTOPBBQ"
#setwd(resultDir)
setwd(file.path(mainDir, resultDir))
QSlink3BBQ <- read_csv("importanceQSlink3LAPTOPBBQwindowsx64.csv",col_types = col_typed)
resetBBQ <- read_csv("test after which reset.csv")
names(resetBBQ)<-c("date","model","task","fold","cv","arch","arch2","pc")
#summary(QSlink3ACE[,1:30])
 #spec(QSlink3BBQ)
 prBBQ<-problems(QSlink3BBQ)
 unique(prBBQ$actual)
 #prBBQ[!str_detect(prBBQ$actual,"columns"),] 
 rowrem<-prBBQ[!str_detect(prBBQ$actual,"columns"),]$row
 QSlink3BBQ<-QSlink3BBQ[-rowrem,]
 setwd(file.path(mainDir))

```
tibble into data.table
```{r}

require(data.table)
DF<-as.data.table(QSlink3ACE)
DF1<-as.data.table(QSlink3HOP)
DF2<-as.data.table(QSlink3BBQ)

DF<-rbindlist(list(DF,DF1,DF2),fill = T)

rm(DF1,DF2,QSlink3BBQ,QSlink3HOP,QSlink3ACE)

reset<-as.data.table(resetACE)
reset1<-as.data.table(resetHOP)
reset2<-as.data.table(resetBBQ)

reset<-rbindlist(list(reset,reset1,reset2),fill = T,idcol=T)
rm(reset1,reset2,resetACE,resetHOP,resetBBQ)
gc()
```
check rename remove nas
```{r}
print("any fails in 4th and fifith coulums? success and transtarg")
sum(str_detect(DF$X4,"FAIL"),na.rm = T)
sum(str_detect(DF$X5,"FAIL"),na.rm = T)
#str(DF)
head(DF)
unique(DF$X13)

DFnam<-c("modelset","model","datetime","success","transTarg","task","missing","append","transform","pc","expirament","fold","maxfold","seed","seedit","foldseed","RMSEmean")
colNum<-T
firCol<-length(DFnam)+1
for (i in (firCol):dim(DF)[2]) {
  if(colNum){
    DFnam<-c(DFnam,paste0("Col",i))
    colNum<-F
  } else {
    DFnam<-c(DFnam,paste0("Val",i))
    colNum<-T
  }
}
names(DF)<-DFnam
summary((DF$Val27))
DF[(is.na(Val29) & is.na(Val27)),]
DF[(is.infinite(Val29)),]
DF<-DF[!(is.na(Val29) & is.na(Val27)),]
DF<-DF[!(is.infinite(Val29)),]
print("summary of first and 4th and 5th valuse")
summary((DF$Val19));summary((DF$Val29));summary((DF$Val27))


```
select best from pessimist file ! not finished just copied from outside
```{r}
load(file="routuDFpessimistUnique.RData")

if(F){
(bestest<-Unq[(1)])
nnd<-which(names(Unq)=="datePOSIX")
strt<-which(names(Unq)=="btp8")
Unqn<-Unq[(is.na(btp11))]
Unqf<-Unq[(!is.na(btp11))]
Unqf[,dum1:=0]
Unqf[,dum2:=0]
Unqf[,dum3:=0]
Unqn[,dum1:=0]
Unqn[,dum2:=0]
Unqn[,dum3:=0]
colord<-names(Unqf)
ol<-length(colord)
(colord<-c(colord[1:strt],colord[(ol-2):ol],colord[(strt+1):(nnd-4)],colord[(nnd):(ol-3)]))
setcolorder(Unqf,colord)
}
```
before melting casting massaging w/e must separate by subject?
otherwise calculation time and memory is huge
poor organization; separated and duplicated results per each recipe into tiddy table
FUNCTION to convert to sparse matrix
```{r}

chosenToSparse<-function(datFr)
{
cols<-which(str_detect(names(datFr),fixed("Col")))
vals<-which(str_detect(names(datFr),fixed("Val")))
(fir<-min(cols))
(endd<-max(cols))
(lst<-max(cols))
if(lst==dim(datFr)[2]) {
  datFr[,(lst):=NULL]
  cols<-cols[-length(cols)]
  lst<-lst-2
}#dim(datFr)
 strt<-fir#names(datFr)[strt]
nnd<-lst+1


prd<-data.table(allColNm=unique(as.vector(datFr[,(cols),with=F][[1]])))
length(unique(datFr$keyVarImp))
i<-unique(datFr$keyVarImp)[10]

for(i in unique(datFr$keyVarImp)){
  wrk<-datFr[(keyVarImp==i)][,(strt:nnd),with=F]
  wrk<-unique(wrk)
  indx<-(unlist(wrk[,seq(by=2,from=1,to=dim(wrk)[2]),with=F]))
  val<-(unlist(wrk[,seq(by=2,from=2,to=dim(wrk)[2]),with=F]))
  unique(indx)
  #unique(val)
  wrk<-data.table(indx,val)
  wrk$val<-as.numeric(wrk$val)
  dim(wrk)
  wrk<-wrk[(order(indx))]
  #wrk[,sdw:=sd(val),by=indx]
  #wrk[,Nw:=.N,by=indx]
  wrk[,val:=mean(val),by=indx]
  wrk<-unique(wrk)
  if(dim(wrk)[1]!=length(unique(wrk$indx))) stop("more work, multiple valuse for same index")
  names(wrk)<-c("indx",paste0(i,"val"))#,paste0(i,"sd"),paste0(i,"N"))
  prd<-merge(prd, wrk,  by.x = "allColNm", by.y = "indx", all = T)
}
return(prd)
}
rm(datFr)
 
 
```

select by task, run choice to sparse,

```{r}
require(stringr)
Unq[,keyVarUnq:=paste0( algomodel, transTarg, task, transform, expirament)]
DF[,keyVarImp:=paste0(modelset, model, transTarg, task, transform, expirament)]
DF[,keyVarUnq:=paste0( model, transTarg, task, transform, expirament)]
(tsks<-unique(Unq$task))
#unique(DF$task)
its<- "QSlinks03_95"#"QSlinks115_60"#tsks[1]
DFs<-DF[(task == its )]
DFs<-DFs[(str_detect(modelset,fixed("hold")) )]
prds<-chosenToSparse(DFs[(keyVarUnq %in% Unq$keyVarUnq)])
#datFr<-DF[(task == its )]
dim(prds)
```
 clean, outliers, features
```{r}
#implemented outlier removal by hand because didn't bother to lookup sparse matrix
lic<-dim(prds)[2]
IQn<-quantile(unlist(prds[,2:lic,with=F]),c(.01,.99),na.rm = T)
IQr<-(IQn[2]-IQn[1])*20
IQn[1]<-IQn[1]-IQr
IQn[2]<-IQn[2]+IQr
if((IQn[2]-IQn[1] > 10)){
wiOut<-names(prds)[which(apply(prds[,2:lic,with=F],2,max,na.rm=T)>IQn[2] | apply(prds[,2:lic,with=F],2,min,na.rm=T)< IQn[1])+1]
i<-wiOut[1]
for(i in wiOut){
  toobig<-as.vector(prds[,i,with=F]>IQn[2])
  toobig[is.na(toobig)]<-F
  prds[(toobig),(i):=IQn[2]]
  toobig<-as.vector(prds[,i,with=F]<IQn[1])
  toobig[is.na(toobig)]<-F
  prds[(toobig),(i):=IQn[1]]
} 
}
nonna<-function(x){
  return(sum(!is.na(x)))
}  
prds$countVar<-apply(prds[,2:lic,with=F],1,nonna)
prds$minVar<-apply(prds[,2:lic,with=F],1,min,na.rm=T)
prds$maxVar<-apply(prds[,2:lic,with=F],1,max,na.rm=T)
prds$meanVar<-apply(prds[,2:lic,with=F],1,mean,na.rm=T)
```
plots to understand Varimp
```{r}

plot(prds$countVar, prds$maxVar)
plot(prds$countVar, prds$meanVar)
hist(prds$countVar)
hist(prds$meanVar)
plot(prds$minVar, prds$maxVar)
plot(prds$meanVar, prds$maxVar)
#prds[(order(meanVar))]$allColNm
```
at this point about to give up because converting column names would be hard and code to fix exists but lets see it anyway
```{r}
actNamesQSlinks03_95 <- c("page","searxinstance","tries","success","time","isPDF","enginebing","engineduckduckgo","enginefaroo","engineggl","enginegoogle","enginegoogle_scholar","enginemojeek","engineyacy","engineyahoo","string.connectordb.","string.markwk.","string.open.humans.","string.open.mhealth.","string.personal_dashboard.","stringBiofourmis","stringBodyTrack","stringconnectordb.io","stringexist.io","stringFitnessSyncer.fluxtream","stringFitnessSyncer.HealthKit","stringFitnessSyncer.zenobase","stringfluxtream.zenobase","stringHealthKit","stringHealthKit.BodyTrack.exist.io","stringHealthKit.BodyTrack.humanapi.co","stringHealthKit.BodyTrack.open.humans"," "," "," "," "," "," ","stringHealthKit.fluxtream.zenobase","stringHealthKit.humanapi.co.betterself.io","stringHealthKit.humanapi.co.connectordb.io","stringHealthKit.humanapi.co.gyrosco.pe","stringHealthKit.humanapi.co.open.humans","stringHealthKit.humanapi.co.open.mhealth","stringHealthKit.humanapi.co.openhumans.org","stringHealthKit.humanapi.co.openmhealth.org","stringHealthKit.tapiriik.connectordb.io","stringHealthKit.tapiriik.gyrosco.pe","stringHealthKit.tapiriik.open.mhealth","stringHealthKit.tapiriik.zenobase","stringHealthKit.tictrac.exist.io","stringHealthKit.tictrac.fluxtream","stringHealthKit.tictrac.gyrosco.pe","stringHealthKit.tictrac.humanapi.co","stringHealthKit.tictrac.open.humans","stringHealthKit.tictrac.open.mhealth","stringHealthKit.tictrac.zenobase","stringHealthKit.validic.BodyTrack","stringHealthKit.validic.exist.io","stringHealthKit.validic.fluxtream","stringHealthKit.validic.gyrosco.pe","stringHealthKit.validic.humanapi.co","stringHealthKit.validic.open.humans","stringHealthKit.validic.open.mhealth","stringHealthKit.validic.openmhealth.org","stringHealthKit.validic.tictrac","stringHealthKit.validic.zenobase","stringHealthKit.zenobase.betterself.io","stringHealthKit.zenobase.connectordb.io","stringHealthKit.zenobase.gyrosco.pe","stringHealthKit.zenobase.open.humans","stringHealthKit.zenobase.open.mhealth","stringHealthKit.zenobase.openmhealth.org","stringhealthvault","stringopen.mhealth","stringopenhumans.org","stringopenmhealth.org","stringpersonal_dashboard","stringqs_ledger","stringtictrac","stringtsubery.quantifier","stringvalidic","sCntQstr","sCntEngine","sRareSite","sRareQstr","sRareEngine","s.score","sRank","sStrongSubQstr","searchCount","sSearchBrevity","sRareSiteBySearch","sSimpleBySearch","sLinProBySearch","sDnchar","sDiNA","fluxtream","healthvault","tapiriik","tictrac","humanapi.co","zenobase","exist.io","quantimodo","openmhealth.org","betterself.io","connectordb.io","connectordb","qs_ledger","tsubery","quantifiedmind","habitica","vitadock","openhumans","humanapi","openmhealth","sDCountWords","sDUWfract","sDUWlog","sDUWsqrt","pageMin","pageMax","searxinstanceMax","triesMax","successMax","timeMax","enginebingMax","engineduckduckgoMax","enginegglMin","enginegglMax","enginegoogleMax","enginegoogle_scholarMax","enginemojeekMax","engineqwantMax","engineredditMax","engineseznamMax","enginestartpageMax","engineyacyMax","engineyahooMax","string.connectordb.Min","string.connectordb.Max","string.markwk.Max","string.open.humans.Min","string.open.humans.Max","string.open.mhealth.Max","string.personal_dashboard.Max","stringBodyTrackMax","stringconnectordb.ioMin","stringexist.ioMax","stringFitnessSyncerMax","stringfluxtreamMin","stringfluxtreamMax","stringfluxtream.zenobaseMax","stringHealthKitMin","stringHealthKit.BodyTrack.connectordb.ioMax","stringHealthKit.BodyTrack.exist.ioMax","stringHealthKit.BodyTrack.humanapi.coMax","stringHealthKit.BodyTrack.open.humansMax"," "," "," "," stringHealthKit.BodyTrack.zenobaseMax","stringHealthKit.fluxtream.exist.ioMax","stringHealthKit.fluxtream.open.humansMax","stringHealthKit.fluxtream.open.mhealthMax","stringHealthKit.fluxtream.openhumans.orgMax","stringHealthKit.fluxtream.openmhealth.orgMax","stringHealthKit.fluxtream.zenobaseMax","stringHealthKit.healthvaultMax","stringHealthKit.humanapi.co.gyrosco.peMax","stringHealthKit.humanapi.co.open.mhealthMax","stringHealthKit.humanapi.co.openhumans.orgMax")#
otherhalf <- c("stringHealthKitlthMin","stringHeargMax","stringHealthKit.humanapitsubery.quantifierMax","stringHealthKit.tapiriik.gyrosco.peMax","stringHealthKit.tapiriik.open.mhealthMax","stringHealthKit.tapiriik.zenobaseMax","stringHealthKit.tictrac.exist.ioMax","stringHealthKit.tictrac.fluxtreamMax","stringHealthKit.tictrac.gyrosco.peMax","stringHealthKit.tictrac.humanapi.coMax","stringHealthKit.tictrac.openhumans.orgMax","stringHealthKit.tictrac.openmhealth.orgMax","stringHealthKit.tictrac.zenobaseMax","stringHealthKit.validic.BodyTrackMax","stringHealthKit.validic.connectordb.ioMax","stringHealthKit.validic.exist.ioMax","stringHealthKit.validic.fluxtreamMax","stringHealthKit.validic.gyrosco.peMax","stringHealthKit.validic.humanapi.coMax","stringHealthKit.validic.markwkMax","stringHealthKit.validic.open.humansMax","stringHealthKit.validic.open.mhealthMax","stringHealthKit.validic.openhumans.orgMax","stringHealthKit.validic.openmhealth.orgMax","stringHealthKit.validic.tictracMax","stringHealthKit.validic.zenobaseMax","stringHealthKit.zenobase.betterself.ioMax","stringHealthKit.zenobase.gyrosco.peMin","stringHealthKit.zenobase.gyrosco.peMax","stringHealthKit.zenobase.markwkMax","stringHealthKit.zenobase.open.humansMax","stringHealthKit.zenobase.openmhealth.orgMax","stringHealthKit.zenobase.quantimodoMax","stringHealthKit.zenobase.tsubery.quantifierMin","stringhealthvaultMax","stringhuman.apiMax","stringmyfitnesspalMax","stringopen.mhealthMax","stringopenhumans.orgMax","stringopenmhealth.orgMin","stringqs_ledgerMax","stringquantimodoMin","stringvalidicMax","stringzenobaseMax","sRareQstrMin","sRareQstrMax","sRareEngineMax","sRankMin","searchCountMin","searchCountMax","sSearchBrevityMin","sRareSiteBySearchMin","sRareSiteBySearchMax","sSimpleBySearchMin","sSimpleBySearchMax","sLinProBySearchMin","sLinProBySearchMax")
#
#print(actNamesQSlinks03_95)
#print(otherhalf)
actNamesQSlinks03_95<-c(actNamesQSlinks03_95,otherhalf)
```

```{r}
actNamesQSlinks115_60<-c("page","tries","isPDF","engineduckduckgo","enginegoogle","engineyahoo","stringBiofourmis","stringFitnessSyncer.HealthKit","stringHealthKit.BodyTrack.exist.io","stringHealthKit.BodyTrack.humanapi.co","stringHealthKit.fluxtream.open.humans","stringHealthKit.fluxtream.open.mhealth","stringHealthKit.humanapi.co.connectordb.io","stringHealthKit.humanapi.co.open.mhealth","stringHealthKit.humanapi.co.openmhealth.org","stringHealthKit.tictrac.fluxtream","stringHealthKit.tictrac.humanapi.co","stringHealthKit.tictrac.open.mhealth","stringHealthKit.validic.BodyTrack","stringHealthKit.validic.exist.io","stringHealthKit.validic.gyrosco.pe","stringHealthKit.validic.humanapi.co","stringHealthKit.validic.open.mhealth","stringHealthKit.validic.openmhealth.org","stringHealthKit.zenobase.betterself.io","stringHealthKit.zenobase.gyrosco.pe","stringHealthKit.zenobase.open.mhealth","sRareSite","sStrongSubQstr","sRareSiteBySearch","sDiNA","healthvault","humanapi.co","vitadock","open mhealth","sDUWfract","pageMin","searxinstanceMax","enginegglMin","enginegoogle_scholarMax","engineyacyMax","stringBodyTrackMax","stringexist.ioMax","stringfluxtream.zenobaseMax","stringHealthKit.BodyTrack.openmhealth.orgMax","stringHealthKit.fluxtream.openmhealth.orgMax","stringHealthKit.humanapi.co.openhumans.orgMax","stringHealthKit.tapiriik.gyrosco.peMax","stringHealthKit.tapiriik.open.mhealthMax","stringHealthKit.tictrac.exist.ioMax","stringHealthKit.tictrac.gyrosco.peMax","stringHealthKit.tictrac.openmhealth.orgMax","stringHealthKit.tictrac.zenobaseMax","stringHealthKit.validic.open.humansMax","stringHealthKit.zenobase.connectordb.ioMax","stringHealthKit.zenobase.gyrosco.peMax","stringHealthKit.zenobase.openmhealth.orgMax","stringzenobaseMax","sRareQstrMax","sSimpleBySearchMin")


for(i in length(actNamesQSlinks03_95):1){
(prds$allColNm<-str_replace(prds$allColNm,paste0("V",i),actNamesQSlinks03_95[i]))
}
prds[(order(meanVar))]$allColNm[1:30]
prds[(order(maxVar))]$allColNm[1:30]
prds[(order(countVar))]$allColNm[1:30]
```
alt mean that equates all ignored with 1
```{r}

i<-names(prds)[-1][17]
for(i in 2:lic){
  tfi<-(as.vector(is.na(prds[,i,with=F])))
  prds[(tfi),(i):=1]
} #prds[(tfi)] #prds[,(i),with=F]
prds$oneMeanVar<-apply(prds[,2:lic,with=F],1,mean,na.rm=T)
plot(prds$oneMeanVar,prds$meanVar)
plot(prds$oneMeanVar,prds$maxVar)
plot(prds$oneMeanVar,prds$countVar)

prds[(order(oneMeanVar))]$allColNm[1:30]
```
what was the varimp formula?
what the 0 -5 and huge + mean?
Bunch of nans and infs
Normalization is a pita; some runs had bigger RMSE ranges because of transform.
maybe should have used min change (mean , median , 0, permute) instead of permutation?
Goal is to approximate importance of this feature to overall model performance but seems like everything overshoots!
```{r}
aggsum<-data.frame(sum=sapply(prds[,2:lic,with=F], sum, na.rm=TRUE),
sd=sapply(prds[,2:lic,with=F], sd, na.rm=TRUE))
plot(aggsum$sd,aggsum$sum)
aggsum$sum[order(aggsum$sum)]
```
what percent of the usefullness of model caused by each feature?
kind of cramming broken data into seemingly good form
ok now I feel like standardizing; all less than 1 set to 1 , log 
subtract 1 from all, divide all by column's sum
```{r}
i<-names(prds)[-1][17]
for(i in 2:lic){
  tfi<-(as.vector((prds[,i,with=F])<1))
  prds[(tfi),(i):=1]
  intrm<-log(prds[,i,with=F])
  intrm<-intrm/sum(intrm)
  prds[,(i):=intrm]
}  
prds$minVarN<-apply(prds[,2:lic,with=F],1,min,na.rm=T)
prds$maxVarN<-apply(prds[,2:lic,with=F],1,max,na.rm=T)
prds$meanVarN<-apply(prds[,2:lic,with=F],1,mean,na.rm=T)
```
now plot it ? 
nope this data is useless. will come back to it whenever i fix and figure out whatever dalex did
```{r}
plot(prds$maxVarN,prds$meanVarN)
plot(prds$oneMeanVar,prds$maxVarN)


prds[(order(maxVarN))]$allColNm[1:30]
prds[(order(meanVarN))]$allColNm[1:30]
```

look for highly uncorrelated recipies
by task select single best model and add to possiblyUniq
then those models that most strongly discorrelate are also added
Since features should be uncorrelated? A rare column effectively used indicates uniqueness? or just cluster?
```{r}

```



