---
title: "Variable importance"
---
load all varimp files and combine into one
```{r}

```
attach missing names from original files
```{r}

```
by task, get all remotley useful variables and graph best ones
```{r}

```
select best from pessimist file ! not finished just copied from outside
```{r}
load(file="routuDFpessimistUnique.RData")
(bestest<-Unq[(1)])
nnd<-which(names(Unq)=="datePOSIX")
strt<-which(names(Unq)=="btp8")
Unqn<-Unq[(is.na(btp11))]
Unqf<-Unq[(!is.na(btp11))]
Unqf[,dum1:=0]
Unqf[,dum2:=0]
Unqf[,dum3:=0]
Unqn[,dum1:=0]
Unqn[,dum2:=0]
Unqn[,dum3:=0]
colord<-names(Unqf)
ol<-length(colord)
(colord<-c(colord[1:strt],colord[(ol-2):ol],colord[(strt+1):(nnd-4)],colord[(nnd):(ol-3)]))
setcolorder(Unqf,colord)

```
by task, get all remotley useful variables and graph best ones
```{r}

```
look for highly uncorrelated recipies
by task select single best model and add to possiblyUniq
then those models that most strongly discorrelate are also added
```{r}

```




